Staged Abstract Interpreters

### 2018-11-17 paper/abstract.tex
abstract

Based on the idea of staged abstract interpreters, we show several case studies, including 
\citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation of 0-CFA, pushdown
control-flow analysis with context/path/flow-sensitivity and store-widening, and a numerical
analysis on an imperative language.

We empirically evaluate the performance improvements on control-flow analysis of benchmark programs.
The results show an average speedup of Nx with staging for a monovariant analysis, and Mx for 
a polyvariant analysis.

>>>>

Based on the idea of staged abstract interpreters, we show several case studies, including 
\citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation of 0-CFA, pushdown
control-flow analysis with context-sensitivity and precise stores, and a numerical
analysis on an imperative language.

We empirically evaluate the performance improvements on control-flow analysis of benchmark programs.
The results show speedups up to 2.3x with staging on a monovariant analysis.
